\textbf{COMP0086 Summative Assignment}

### 2022-11-08 submission.tex
reorganise file structure

\begin{document}
    \maketitle
\begin{enumerate}[leftmargin=\labelsep]
\section{PART I}
\subsection{Linear Regression}
\item[1.]
    \begin{enumerate}
        \item Superimposing the four different curves corresponding to each fit over the four given data points:
        \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.5]{outputs/python/q1/q1a}
        \caption{Data set $\{(1, 3), (2, 2), (3, 0), (4, 5)\}$ fitted with basis $\{1, x\}$ and basis $\{1, x, x^2, x^3\}$ }
        \label{fig:1a}
        \end{figure}

        \item The weights for the equations:
        \begin{center}
        \begin{tabular}{c|c|c|c|c}%
         \textbf{Basis}&\textbf{k=1}&\textbf{k=2}&\textbf{k=3} &\textbf{k=4}% specify table head
        \csvreader[head to column names]{outputs/python/q1/q1b.csv}{}% use head of csv as column names
        {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
        \end{tabular}
        \end{center}

        \item The mean squared error for each fitted curve:
        \begin{center}
        \begin{tabular}{c|c|c|c|c}%
         \textbf{Metric}&\textbf{k=1}&\textbf{k=2}&\textbf{k=3} &\textbf{k=4}% specify table head
        \csvreader[head to column names]{outputs/python/q1/q1c.csv}{}% use head of csv as column names
        {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
        \end{tabular}
        \end{center}
    \end{enumerate}
\newpage
\item[2.]
    \begin{enumerate}
        \item
        \begin{enumerate}
            \item Plotting the function $sin^2(2\pi x)$ in the range $0 \leq x \leq 1$ with the sampled points superimposed:
                    \begin{figure}[h]
                    \centering
                    \includegraphics[scale=0.5]{outputs/python/q2/q2ai}
                    \caption{Noisy samples}
                    \label{fig:2ai}
                    \end{figure}
            \item Fitting the data set with polynomial bases of dimension $k = 2, 5, 10, 14, 18$ and plotting each of these 5 curves with the sampled points superimposed:
                    \begin{figure}[h]
                    \centering
                    \includegraphics[scale=0.5]{outputs/python/q2/q2aii}
                    \caption{Polynomial fit curves}
                    \label{fig:2aii}
                    \end{figure}
        \end{enumerate}
\newpage
        \item Plotting  the natural $\log$ ($\ln$) of the training error versus the polynomial dimension $k = 1, . . . , 18$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/python/q2/q2b}
            \caption{Training Error of Polynomial Curves}
            \label{fig:2b}
            \end{figure}

@@

            \includegraphics[scale=0.5]{outputs/python/q2/q2c}

@@

            \includegraphics[scale=0.5]{outputs/python/q2/q2d}

@@

            \includegraphics[scale=0.5]{outputs/python/q3/q3b}

@@

            \includegraphics[scale=0.5]{outputs/python/q3/q3c}

@@

            \includegraphics[scale=0.5]{outputs/python/q3/q3d}

@@

            \includegraphics[scale=0.5]{outputs/python/q6/q6}

@@

            \includegraphics[scale=0.5]{outputs/python/q7/q7}

@@

            \includegraphics[scale=0.5]{outputs/python/q8/q8}

>>>>

\begin{document}
    \maketitle
\begin{enumerate}[leftmargin=\labelsep]
\section{PART I}
\subsection{Linear Regression}
\item[1.]
    \begin{enumerate}
        \item Superimposing the four different curves corresponding to each fit over the four given data points:
        \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.5]{outputs/q1/q1a}
        \caption{Data set $\{(1, 3), (2, 2), (3, 0), (4, 5)\}$ fitted with basis $\{1, x\}$ and basis $\{1, x, x^2, x^3\}$ }
        \label{fig:1a}
        \end{figure}

        \item The weights for the equations:
        \begin{center}
        \begin{tabular}{c|c|c|c|c}%
         \textbf{Basis}&\textbf{k=1}&\textbf{k=2}&\textbf{k=3} &\textbf{k=4}% specify table head
        \csvreader[head to column names]{outputs/q1/q1b.csv}{}% use head of csv as column names
        {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
        \end{tabular}
        \end{center}

        \item The mean squared error for each fitted curve:
        \begin{center}
        \begin{tabular}{c|c|c|c|c}%
         \textbf{Metric}&\textbf{k=1}&\textbf{k=2}&\textbf{k=3} &\textbf{k=4}% specify table head
        \csvreader[head to column names]{outputs/q1/q1c.csv}{}% use head of csv as column names
        {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
        \end{tabular}
        \end{center}
    \end{enumerate}
\newpage
\item[2.]
    \begin{enumerate}
        \item
        \begin{enumerate}
            \item Plotting the function $sin^2(2\pi x)$ in the range $0 \leq x \leq 1$ with the sampled points superimposed:
                    \begin{figure}[h]
                    \centering
                    \includegraphics[scale=0.5]{outputs/q2/q2ai}
                    \caption{Noisy samples}
                    \label{fig:2ai}
                    \end{figure}
            \item Fitting the data set with polynomial bases of dimension $k = 2, 5, 10, 14, 18$ and plotting each of these 5 curves with the sampled points superimposed:
                    \begin{figure}[h]
                    \centering
                    \includegraphics[scale=0.5]{outputs/q2/q2aii}
                    \caption{Polynomial fit curves}
                    \label{fig:2aii}
                    \end{figure}
        \end{enumerate}
\newpage
        \item Plotting  the natural $\log$ ($\ln$) of the training error versus the polynomial dimension $k = 1, . . . , 18$:
            \begin{figure}[h]
            \centering
            \includegraphics[scale=0.5]{outputs/q2/q2b}
            \caption{Training Error of Polynomial Curves}
            \label{fig:2b}
            \end{figure}

@@

            \includegraphics[scale=0.5]{outputs/q2/q2c}

@@

            \includegraphics[scale=0.5]{outputs/q2/q2d}

@@

            \includegraphics[scale=0.5]{outputs/q3/q3b}

@@

            \includegraphics[scale=0.5]{outputs/q3/q3c}

@@

            \includegraphics[scale=0.5]{outputs/q3/q3d}

@@

            \includegraphics[scale=0.5]{outputs/q6/q6}

@@

            \includegraphics[scale=0.5]{outputs/q7/q7}

@@

            \includegraphics[scale=0.5]{outputs/q8/q8}
